---
title: "Pupil Yes/No Pilot Data Processed using GazeR"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=6, fig.height=4, fig.path='Figs/', echo=TRUE, tidy=TRUE, message=F, warning=F, cache=T)
```

## Install Gazer 
I had some trouble getting this to go and had to mannually install some of the needed packages (ggforce).

library(devtools)
install_github("dmirman/gazer")
library(ggforce)

## Read in data
Pupil data exported as individual reports for each participant and aggregated using merge_pupil function.

```{r }

library(tidyverse)
library(gazer)
library(dplyr)

file_list <-list.files(".", pattern = ".xls")
pupil_files <- merge_pupil(
  file_list,
  blink_colname = "AVERAGE_IN_BLINK",
  pupil_colname = "AVERAGE_PUPIL_SIZE"
)

```

## 'Missingness'
Remove participants AND trials that have greater than a specified threshold of missing values (here 20%)

```{r eval=TRUE, warning=TRUE, error =TRUE, message=TRUE}
pup_missing <- count_missing_pupil(pupil_files, missingthresh = .2)

```

## De-blink

remove blinks AND 100ms window on each side of blink
```{r }
pup_extend<- pup_missing %>% 
  group_by(subject, trial) %>% 
  mutate(extendpupil=extend_blinks(pupil, fillback=100, fillforward=100, hz=1000))

```

## Removing other bad data 
Plot a histogram and visually examine to determine what values are unlikely to be real measurements (based on recommendation by Mathot?). Alternatively we could set a threshold independently.

```{r }

puphist <- ggplot(pup_extend, aes(x = extendpupil)) + 
  geom_histogram(aes(y = ..count..), colour = "green", binwidth = 0.5)  + 
  geom_vline(xintercept = 850, linetype="dotted") +
  geom_vline(xintercept = 1500, linetype="dotted") + 
  xlab("Pupil Size") + 
  ylab("Count") + 
  theme_bw() 

print(puphist)
```

```{r }
pup_outliers <- pup_extend %>% 
  filter(extendpupil >= 850, extendpupil <= 1500)

puphist_noOutliers <- ggplot(pup_outliers, aes(x = extendpupil)) + 
  geom_histogram(aes(y = ..count..), colour = "green", binwidth = 0.5)  + 
  geom_vline(xintercept = 850, linetype="dotted") +
  geom_vline(xintercept = 1500, linetype="dotted") + 
  xlab("Pupil Size") + 
  ylab("Count") + 
  theme_bw() 

print(puphist_noOutliers)
```


## Interpolate 

Performs a linear interpolation of missing values
```{r }
pup_interp <- interpolate_pupil(
  pup_outliers, 
  extendblinks = TRUE, 
  type = "linear")

```

## MAD (speed of dialation)

May need to perform interpolation again after this step. MAD can not be performed with NAs in the dataset; at this time it must occur after interpolation. 

```{r }
mad_removal <- pup_interp %>%
  group_by(subject, trial) %>%
  mutate(speed=speed_pupil(interp,time)) %>%
  mutate(MAD=calc_mad(speed)) %>%
  filter(speed < MAD)

#ggplot(data=mad_removal, aes(x=time, y=interp, colour = factor(subject))) + geom_point() + ylim(400, 1200) + facet_grid(cond ~ .)

```

## Interpolate 

Performs a linear interpolation of missing values
```{r }

pup_interp2 <- interpolate_pupil(
  mad_removal, 
  extendblinks = TRUE, 
  type = "linear")

```

## Smoothing

Using moving average to smooth; window set to 8
```{r }
rolling_mean_pupil_average <- as.data.frame(pup_interp2) %>% #must be in a data.frame
  select(
    subject, trial, pupil, 
    time, interp, sample_message, cond) %>%
  mutate(movingavgpup = moving_average_pupil(interp, n = 8))

```


## Baseline correction

Baseline window set to 1 second long starting at ???
```{r }
baseline_pupil <- baseline_correction_pupil(
  rolling_mean_pupil_average, 
  pupil_colnames = "movingavgpup", 
  baseline_window = c(event = c("Baseline_Onset"), event = c("Baseline_Offset")))

#ggplot(data=baseline_pupil, aes(x=time, y=baselinecorrectedp)) + geom_point() + ylim(-300, 300)
```

## Convert to meaningful units
### (we need to change this formula to fit our setup!!)
uses formula to change from abitrary unit to mm (we need to change this formula to fit our setup!!)

```{r }
timebinsmm <- baseline_pupil  %>% 
  mutate(pupilmm = (sqrt(movingavgpup) * (0.119789246)))

#ggplot(data=timebinsmm, aes(x=time, y=pupilmm)) + geom_point() + 
```

## Change trial onset to Zero

```{r }
baseline_pupil_onset <- timebinsmm %>% 
  group_by(subject, trial) %>%  
  mutate(time_zero= onset_pupil(time, sample_message, event = c("Stimulus_Onset") )) %>%
  ungroup() %>% 
  filter(time_zero >= 0, time_zero <= 15000) %>%
  select(
    subject, trial, time, time_zero, 
    sample_message, pupilmm, cond)

#ggplot(data=baseline_pupil_onset, aes(x=time_zero, y=pupilmm)) + geom_point() 
```


## Binning and aggregating 

Adds column assinging bins. Bin length set here to 250ms.

```{r }

timebins1 <- downsample_pupil(baseline_pupil_onset, bin.length=250)

head(timebins1)
```

Group and summarize according to bin by condition

```{r }
agg_subject <- timebins1 %>% 
  dplyr::group_by(subject, cond, timebins) %>% 
  dplyr::summarise(aggbaseline=mean(pupilmm)) %>% 
  ungroup()
  
```

## Plotting

```{r }
plotByCond <- ggplot(agg_subject, aes(timebins, aggbaseline, color = subject)) +
  geom_smooth(method = loess) + facet_grid(.~ cond)
  
print(plotByCond)
  
```
