---
title: "Resting State PreProcessing using GazeR"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=6, fig.height=4, fig.path='Figs/', echo=TRUE, tidy=TRUE, message=F, warning=F, cache=T)
```

## 15 second subset of data for demonstration purposes

Read in and plot the data

```{r }

library(tidyverse)
library(gazer)

bz4min <-read.csv("bz4gazer.csv", header =T)


pup_files1 <-arrange(bz4min, subject, trial, time) %>% 
  filter(time>= 0, time <= 15000)

ggplot(data=pup_files1, aes(x=time, y=pupil)) + geom_point() + ylim(400, 1200)
```

```{r eval=TRUE, warning=TRUE, error =TRUE, message=TRUE}
pup_missing <- count_missing_pupil(pup_files1, missingthresh = .2)

```

## De-blink

remove blinks AND 100ms window on each side of blink
```{r }
pup_extend<- pup_missing %>% 
  group_by(subject, trial) %>% 
  mutate(extendpupil=extend_blinks(pupil, fillback=100, fillforward=100, hz=1000))

ggplot(data=pup_extend, aes(x=time, y=extendpupil)) + geom_point() + ylim(400, 1200)
```

## Removing other bad data 
### High band set low (1100) for demo purpose
Unsure where this should go. Would be more informative after convertion to mm.
If there are outliers there we will have to remove them and go through the process again starting at interpolation. 

```{r }

puphist <- ggplot(pup_extend, aes(x = extendpupil)) + 
  geom_histogram(aes(y = ..count..), colour = "green", binwidth = 0.5)  + 
  geom_vline(xintercept = 100, linetype="dotted") +
  geom_vline(xintercept = 1200, linetype="dotted") + 
  xlab("Pupil Size") + 
  ylab("Count") + 
  theme_bw() 

print(puphist)
```

### High band set low (1100) for demo purpose

```{r }
pup_outliers <- pup_extend %>% 
  mutate(extendpupil = replace(extendpupil, extendpupil<= 0 | extendpupil >= 1100, NA))

ggplot(data=pup_outliers, aes(x=time, y=extendpupil)) + geom_point() + ylim(400, 1200)
```



## Interpolate 

performs a linear interpolation of missing values
```{r }
pup_interp <- interpolate_pupil(
  pup_outliers, 
  extendblinks = TRUE, 
  type = "linear")

ggplot(data=pup_interp, aes(x=time, y=interp)) + geom_point() + ylim(400, 1200)

```
## MAD (speed of dialation)

May need to perform interpolation again after this step. MAD can not be performed with NAs in the dataset; at this time it must occur after interpolation. 

```{r }
mad_removal <- pup_interp %>%
  group_by(subject, trial) %>%
  mutate(speed=speed_pupil(interp,time)) %>%
  mutate(MAD=calc_mad(speed)) %>%
  filter(speed < MAD)

ggplot(data=mad_removal, aes(x=time, y=interp)) + geom_point() + ylim(400, 1200)

```


## Smoothing
### (currectly set to 20 for demo purposes)
uses a moving average to smooth 
```{r }
rolling_mean_pupil_average <- as.data.frame(pup_interp) %>% #must be in a data.frame
  select(
    subject, trial, pupil, 
    time, interp, sample_message) %>%
  mutate(movingavgpup = moving_average_pupil(interp, n = 20))

ggplot(data=rolling_mean_pupil_average, aes(x=time, y=movingavgpup)) + geom_point() + ylim(400, 1200)
```

## Baseline correction

Baseline window set to 1 second long starting at ???
```{r }
baseline_pupil <- baseline_correction_pupil(
  rolling_mean_pupil_average, 
  pupil_colnames = "movingavgpup", 
  baseline_window = c(0, 1000))

ggplot(data=baseline_pupil, aes(x=time, y=baselinecorrectedp)) + geom_point() + ylim(-300, 300)
```

## Convert to meaningful units
### (we need to change this formula to fit our setup!!)
uses formula to change from abitrary unit to mm (we need to change this formula to fit our setup!!)
```{r }
timebinsmm <- rolling_mean_pupil_average  %>% 
  mutate(pupilmm = (movingavgpup * 5)/5570.29)

ggplot(data=timebinsmm, aes(x=time, y=pupilmm)) + geom_point() + ylim(.5, 1.1)
```


## Change trial onset to Zero

```{r }
baseline_pupil_onset <- timebinsmm %>% 
  group_by(subject, trial) %>%  
  mutate(time_zero= onset_pupil(time, sample_message, event = c("Simple_Start") )) %>%
  ungroup() %>% 
  filter(time_zero >= 0, time_zero <= 15000) %>%
  select(
    subject, trial, time, time_zero, 
    sample_message, pupilmm)

ggplot(data=baseline_pupil_onset, aes(x=time_zero, y=pupilmm)) + geom_point() + ylim(.5, 1.1)
```

## Binning
adds column assinging bin
```{r }
timebins1 <- downsample_pupil(baseline_pupil_onset, bin.length=200)

head(timebins1)
```

groups and summarizes on bins

```{r }
agg_subject<- timebins1 %>% 
  dplyr::group_by(subject,timebins) %>% 
  dplyr::summarise(aggbaseline=mean(pupilmm)) %>% 
  ungroup()

ggplot(data=agg_subject, aes(x=timebins, y=aggbaseline)) + geom_point() + geom_line(size = 1) + ylim(.5, 1.1)
```
